\documentclass[10pt,a4paper,sans]{moderncv}

\moderncvstyle{classic}    
\moderncvcolor{blue}  
\usepackage[top=0.75in, bottom=0.75in, left=0.75in, right=0.75in, scale=0.75]{geometry}

\usepackage{setspace}
\usepackage[backend=bibtex, style=ieee]{biblatex}
\bibliography{tech}
\usepackage[english]{babel}

\firstname{Agata U.}
\familyname{Kargol}
\address{4555 39th Ave SW Apt B418}{Seattle, WA 98116}
\email{aukargol@gmail.com}
                
%\photo[64pt][0.4pt]{example-image-a}              
                       
\renewcommand*{\cventry}[7][.25em]{%
  \cvitem[#1]{#2}{%
    {\bfseries#3}%
    \ifthenelse{\equal{#4}{}}{}{ \hfill{\slshape#4}}%
    \ifthenelse{\equal{#5}{}}{}{ #5}%
    \ifthenelse{\equal{#6}{}}{}{ #6}%
    \strut%
    \ifx&#7&%
      \else{\newline{}\begin{minipage}[t]{\linewidth}\small#7\end{minipage}}\fi}}

\begin{document}
\makecvtitle
\vspace{-3em}
\section{Objective}
Seeking Software Developer position in the Seattle, WA area. Python 2 and 3, RESTful API development, full-stack web development, robotics, computer vision.

\vspace{-0.3em}
\section{Education}
\vspace{-0.3em}
\cventry{May 2015}{Master of Science in Computer Science}{}{}{\hfill \textit{NSF Graduate Research Fellow}}{\textit{Washington University in St. Louis}, St. Louis, MO\\ \textbf{Select Coursework:} Mobile Robotics, Computer Vision, Machine Learning}
\cventry{May 2011}{Bachelor of Science in Computer Science}{}{}{\hfill \textit{cum laude}}{\textit{University of Alabama}, Tuscaloosa, AL \\ \textbf{Minors:} Mathematics, Computer-Based Honors Program, Telecommunication and Film }

\vspace{-0.3em}
\section{Skills}
\vspace{-0.3em}
\cvitem{Languages}{
\begin{itemize}
\item \textbf{Native:} English, Polish
\item \textbf{Proficient:} Python2, Python3, JavaScript, SQL
\item \textbf{Past:} Matlab, C, C++, bash
\end{itemize}
}
\vspace{-1.2em}
\cvitem{Frameworks}{Flask, Pyramid, Django, SQLAlchemy, alembic, pytest, pandas, celery}
\cvitem{Technologies}{PyCharm, git (preferred), SVN, mercurial, *nix, PostgreSQL, RabbitMQ, Redis, Cassandra, Jenkins}

\vspace{-0.3em}
\section{Professional Experience}
\vspace{-0.3em}
\cventry{2015-2017}{Software Development Engineer}{Zonar Systems, Inc.}{Seattle, WA}{}{
\begin{itemize}
\item Zonar Systems is a vehicle telematics company providing fleet management solutions. Member of Pupil Team, which focused on school bus related solutions for parents, dispatchers, and school administrators.
\item Built \textit{MyBusVue}, a parent facing web app which provides near-real time bus tracking and student scan information.
Architected and built \textbf{RESTful API} powering parent-facing web app, Android app, iOS app, as well as dispatcher tools.
Stack includes \textbf{Python2 (ported to Python3), pyramid, SQLAlchemy, JavaScript, Angular 1.5, celery, Postgres, Cassandra, and Redis}.
\item Worked on \textit{Rider Verification}, a bus driver and dispatcher facing solution to provide information about where students should be in real-time. Worked on both \textbf{RESTful API} layer and \textbf{ETL} process to ingest data from multiple sources (internal and external integration). Stack includes \textbf{Python3, flask, SQLAlchemy, Postgres, Angular 1.6, pandas}.
\end{itemize}
}

\cventry{2011-2015}{Graduate Research Assistant}{Washington Univ. in St. Louis}{}{}{
	\vspace{-0.5em}
	\normalsize \hspace{-3em} \textit{Archive of Many Outdoor Scenes (AMOS) Development}
	\vspace{0.2em}
	\small
	\begin{itemize}
		\item Worked AMOS, the world's largest archive of outdoor webcams, which contains over 500 million images
		\item Built and managed AMOS crowdsourced tasks with Amazon Mechanical Turk
		\item Developed backend features and optimizations as part of a team
		\item Django, Python2, JavaScript, Matlab, AWS Mechanical Turk
	\end{itemize} 
	\vspace{0.3em}
	\normalsize \hspace{-3em} \textit{Pedestrian Detection in Webcam Imagery for Public Health Applications} 
	\vspace{0.2em}
	\small
	\begin{itemize}
		\item Explored use of existing machine learning tools and algorithms for pedestrian detection in webcams
		\item Improved detection algorithms through background subtraction and shadow detection methods
	\end{itemize}
	\vspace{0.3em}
	\normalsize \hspace{-3em} \textit{Point-and-click Object Manipulation Interface for PR2 Robot} 
	\vspace{0.2em}
	\begin{itemize}
   		\item Developed point-and-click interface for object manipulation for Willow Garage's PR2 robot to allow the PR2 to act a surrogate for a paraplegic user
		\item Learned about robot functionality and limitations, interface design based on user requirements, and the mathematical concepts of robot visual processing
		\item Required ROS, Python, C++, Qt framework, OpenCV
	\end{itemize}
}

\vspace{-0.3em}
\nocite{*}
\begingroup
\setstretch{0.5}
\setlength\bibitemsep{0.3em}
\printbibliography[title= Select Publications]
\endgroup

\vspace{-1em}
\section{Outreach and Leadership}
\vspace{-0.3em}
\cvitem[0em]{2013}{Invited expert panelist on \textit{"Frameworks to Guide Image Annotations"} at \textit{SenseCam}}
\cvitem[0em]{2012}{Participated in the PR2 Workshop held in Freiburg, Germany}


\end{document}

